Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and correlation with baryon disk properties

### 2019-07-16 Document/paper.tex
edit tables

\begin{figure*}
\begin{center}
  \subfloat[DM shape at small radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_A_DM.pdf}} 
  \subfloat[DM shape at large radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_A_MHD.pdf}} 
\end{center}
\caption{}
\label{fig:triaxial_history}
\end{figure*}

\begin{figure*}
\begin{center}
  \subfloat[DM shape at small radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_B_DM.pdf}} 
  \subfloat[DM shape at large radius]{\includegraphics[width=0.4\textwidth]{Z_Triax_level3_set_B_MHD.pdf}} 
\end{center}
\caption{}
\label{fig:triaxial_history}
\end{figure*}

@@

%\subsection{The solid ellipsoid method}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{cumulative_alignment.pdf}
\caption{Cumulative distribution of alignment $\cos\theta$ between the
  minor axis of the dark matter halo at different radii and the
  stellar disk.} \label{fig:alignment_out}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{delta_T_correlations.pdf}
\caption{Changes in the triaxiality at $R_{\rm vir}/8$ as a function of different halo and disk properties.}
\label{fig:sphericity}
\end{figure*}

\textbf{Actually we have not examined the relation of c/a in MHD halos
  with some measure of c/a from the disk, that is something like
  Zdisk/Rdisk. This actually would make more sense from a physical
  point of view: effect of the potential. }

@@

\subsection{Comparison against observational constraints}

\begin{table*}
\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
Reference&$q_{\rho}$&$s_{\rho}$&$R$&$\theta$&
Methodology\\ 
\hline \hline \citet{Olling_and_Merrifield_2000}& $1.00$
& $0.80$ &  $\simeq 8$kpc & $0^{\circ}$&Stellar dynamics and HI
density. \\

\multirow{2}{*}{\citet{Banerjee_and_Chanda_2011}}&${1}$&${1}$&$9$kpc&$0^{\circ}$&Method:
HI
gas. \\ &${0.5}$&${0.5}$&$24$kpc&$0^{\circ}$&Monotonical
change between radial regimes.\\

\citet{Loebman_et_al._2012}&${1.00}$&${0.47}$&$\sim
20$kpc &$0^{\circ}$&Method: SDSS statistics\\

\cite{Johnston_et_al._2005}&${1}$&$0.83-0.92$&$\lesssim
60$kpc&$0^{\circ}$&Method: Sagittarius stream\\

\citet{Bovy_et_el._2016}&${0.95}$&${0.95}$&$\lesssim
20$kpc&$90^{\circ}$ & Stellar streams\\

\citet{Deg_and_Widrow_2013}&$0.72$&$0.28$&
$20$kpc-$60$kpc$ $&$90^{\circ}$&
Mid-axis orientation. Sagittarius stream\\\hline\hline

\citet{Abadi_et_al._2010} &${0.98}$&${0.85}$& & & Simulations. Almost
  independent of radius. No feedback: boundary case\\\hline

\end{tabular}
\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
    esta medido theta?}}
\end{table*}

\begin{table*}
\begin{tabular}{|l|cc|c|c|p{7cm}|}\hline
Reference&$q_{\phi}$&$s_{\phi}$&$R$&$\theta$&
Methodology\\ \hline \hline

\citet{Bowden_et_al._2016}& 0.5-0.66 &0.5-0.66& 5kpc - 10 kpc& $90^{\circ}$&
Weak constraint on prolate halo. SDSS stars dynamics.\\

\multirow{2}{*}{\citet{Vera-Ciro_and_Helmi_2013}}&${1.00}$&${0.90}$&$\lesssim
10$kpc&$0^{\circ}$ & Sagittarius stream \& LMC \\
&${0.90}$&${0.80}$&$\gtrsim 10$kpc&$90^{\circ}$&
Mid-axis orientation on the outside. \\

\citet{Law_and_Majewski_2009}&${0.83}$&${0.67}$&
$\lesssim 60$kpc&$90^{\circ}$&Mid-axis orientation. Sagittarius
stream\\

\citet{Law_and_Majewski_2010}&${0.99}$&${0.72}$&
$20$kpc-$60$kpc$$&$90^{\circ}$&Mid-axis orientation, Sagittarius
stream\\

\citet{Deg_and_Widrow_2013} & $0.82$&$0.40$&
$20$kpc $60$kpc$ $&$90^{\circ}$&
Mid-axis orientation. Sagittarius stream\\\hline \hline

\citet{Chua_et_al._2018}&${0.88\pm0.10}$&${0.70\pm0.11}$&$0.15R_{200}$&
& Illustris\\

\citet{Bryan_et_al._2013}&$0.84-0.86$&$0.66-0.70$&$R_{200}$& & 
For different cosmologies and feedback recipies. Calculated from a fit
at $M_\odot=10^12$\\\hline

\end{tabular}
\caption{{\bf Cuales son las incertidumbres? Con respecto a que eje
    esta medido theta?}}
\end{table*}
%\end{multicols}

>>>>

\begin{figure*}
\begin{center}
  \subfloat[DM shape at small radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_DM.pdf}} 
  \subfloat[DM shape at large radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_A_MHD.pdf}} 
\end{center}
\caption{}
\label{fig:triaxial_history_A}
\end{figure*}

\begin{figure*}
\begin{center}
  \subfloat[DM shape at small radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_DM.pdf}} 
  \subfloat[DM shape at large radius]{\includegraphics[width=0.35\textwidth]{Z_Triax_level3_set_B_MHD.pdf}} 
\end{center}
\caption{}
\label{fig:triaxial_history_B}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
\end{center}
\caption{A}
\label{fig:disk_correlations}
\end{figure*}

\begin{figure}
\begin{center}
\includegraphics[width=0.45\textwidth]{triaxiality_observations.pdf}
\end{center}
\caption{A}
\label{fig:observations}
\end{figure}

@@

@@

@@

@@
